---
title: "Facs analysis"
author: Alexis Hucteau
date: "`r Sys.Date()`"
output:
    html_document:
      toc: yes
      toc_float: yes
      theme: united
editor_options:
  markdown:
    wrap: sentence
---

Back to [PhD Project](https://alexishucteau.github.io/PhD_project/)

```{r, include=F, echo=F}
library(ggplot2)
library(dplyr)

Diff_facs_analysis <- read.csv("Data/Replicat 1/Diff_AGI.csv")
Rhod2_facs_analysis <- read.csv("Data/Replicat 1/Rhod2_AGI.csv")
PpIX_facs_analysis <- read.csv("Data/Replicat 1/PpIX_AGI_ALA_Basal.csv")
Scenith_analysis <- read.csv("Data/Replicat 1/Scenith.csv")

# -----------------------

Replicat2 <- read.csv("Data/Replicat 2/2021 12 14 - Rhod2 - M14R132, 56-11 AGI J+7.csv", nrows = 10, check.names = F, row.names = 1)[,-6]

Rhod2_df <- data.frame("Rhod2" = Replicat2$`Median Rhod2`[c(1:4)],
                       "Cell.line" = c(rep("56-11",2), rep("M14",2)),
                       "Treatment" = rep(c("AGI", "DMSO"), 2)) %>% 
  t() %>%
  data.frame() %>%
  rev() %>% 
  t() %>%
  data.frame() 

CD38_df <- data.frame("CD38" = Replicat2[c(1:4),"Median CD38"],
                      "Cell.line" = c(rep("56-11", 2), rep("M14", 2)),
                      "Treatment" = rep(c("AGI", "DMSO"), 2))

CD15_df <- data.frame("CD15" = Replicat2[c(1:4),"Median CD15"],
                      "Cell.line" = c(rep("56-11", 2), rep("M14", 2)),
                      "Treatment" = rep(c("AGI", "DMSO"), 2)
                      )

Scenith_replicat_2 <- data.frame("Cell.line" = c(rep("M14", 2), rep("56-11",2)),
                             "Mitochondrial_dependancy" = c(62.9, 16.0, 46.7, 40.8),
                             "Mitochondrial_signal" = c(199824.95, 251765.25, 557897, 450958.25),
                             "Treatment" = rep(c("DMSO", "AGI"), 2)
)
```

# Summary

* [Rhod2](#rhod2)
* [PpIX](#ppix)
* [PPIX flux](#ppix-flux)
* [Scenith](#scenith)
  * [Glycolyse dependency](#glycolyse)
  * [Mitochondria dependency](#mito)
* [Differenciation](#diff)
  * [CD11b](#cd11b)
  * [CD14](#cd14)
  * [CD15](#cd15)

# Rhod2, calcium indicator {#rhod2}

## Replicat 1

```{r, echo=F}
ggplot(data=Rhod2_facs_analysis, aes(x = Cell.line, y = Rhod2, color = factor(Treatment, levels = c("DMSO", "AGI")))) +
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Calcium indicator", x = "Cell lines")+
  theme_minimal()
```

## Replicat 2

```{r, echo=F}
ggplot(data=Rhod2_df, aes(x = Cell.line, y = as.numeric(Rhod2), color = factor(Treatment, levels = c("DMSO", "AGI")))) +
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Calcium indicator", x = "Cell lines")+
  theme_minimal()
```

## Replicat 3

```{r, echo=F}
Rhod2_rep3 <- data.frame("Rhod2" = c(4084,3896, 1737, 2140),
                        "Cell.line" = c("56-11", "56-11", "Molm14", "Molm14"),
                        "Treatment" = c("DMSO", "AGI", "DMSO", "AGI"))

ggplot(data=Rhod2_rep3, aes(x=Cell.line, y=Rhod2, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Calcium indicator", x = "Cell lines")+
  theme_minimal()
```



# PpIX {#ppix}

```{r, echo=F}
ggplot(data=PpIX_facs_analysis, aes(x = Cell.line, y = MFI_PpIX, color = factor(Treatment, levels = c("DMSO", "AGI")))) + 
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "PpIX indicator", x = "Cell lines")+
  theme_minimal()
```

# PpIX flux (ALA/basal) {#ppix-flux}

```{r, echo=F}
ggplot(data=PpIX_facs_analysis, aes(x = Cell.line, y = ALA.basal, color = factor(Treatment, levels = c("DMSO", "AGI")))) + 
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "PpIX ALA/basal", x = "Cell lines")+
  theme_minimal()
```

# Scenith {#scenith}

PDF files:

* [M14 + DMSO](https://alexishucteau.github.io/PhD_project/Analysis/Wetlab/Data/Scenith_M14R132_DMSO.pdf)
* [M14 + AGI](https://alexishucteau.github.io/PhD_project/Analysis/Wetlab/Data/Scenith_M14R132_AGI.pdf)

## Glycolyse dependency {#glycolyse}

```{r, echo=F}
ggplot(data=Scenith_analysis, aes(x=factor(Treatment, levels = c("DMSO", "AGI")), y=Gly_dependency, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Glycolyse dependency", x = "Treatment")+
  theme_minimal()
```

## Mitochondria dependency {#mito}

### Replicat 1

```{r, echo=F}
ggplot(data=Scenith_analysis, aes(x=factor(Treatment, levels = c("DMSO", "AGI")), y=Mito_dependency, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Mitochondria dependency", x = "Treatment")+
  theme_minimal()
```

### Replicat 2

```{r, echo=F}
ggplot(data=Scenith_replicat_2, aes(x=Cell.line, y=Mitochondrial_dependancy, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "Mitochondria dependency", x = "Treatment")+
  theme_minimal()
```

# Differenciation markers {#diff}

## CD11b {#cd11b}

```{r, echo=F}
ggplot(data=Diff_facs_analysis[c(1:4),], aes(x=Cell.line, y=CD11b_PE_A, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD11b", x = "Cell lines")+
  theme_minimal()
```

## CD14 {#cd14}

```{r, echo=F}
ggplot(data=Diff_facs_analysis[c(1:4),], aes(x=Cell.line, y=CD14.APC__A700_A, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD14", x = "Cell lines")+
  theme_minimal()
```

## CD15 {#cd15}

### Replicat 1

```{r, echo=F}
ggplot(data=Diff_facs_analysis[c(1:4),], aes(x=Cell.line, y=CD15_APC_A, color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD15", x = "Cell lines")+
  theme_minimal()
```

### Replicat 2

```{r, echo=F}
ggplot(data=CD15_df, aes(x=Cell.line, y=as.numeric(CD15), color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD15", x = "Cell lines")+
  theme_minimal()
```

### Replicat 3

```{r, echo=F}
CD15_rep3 <- data.frame("CD15" = c(4986,3977,1504,1558),
                        "Cell.line" = c("56-11", "56-11", "Molm14", "Molm14"),
                        "Treatment" = c("DMSO", "AGI", "DMSO", "AGI"))

ggplot(data=CD15_rep3, aes(x=Cell.line, y=as.numeric(CD15), color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD15", x = "Cell lines")+
  theme_minimal()
```



# CD38

## Replicat 1

```{r, echo=F}
CD38_df <- data.frame("CD38" = Replicat2[c(1:4),"Median CD38"],
                      "Cell.line" = c(rep("56-11", 2), rep("M14", 2)),
                      "Treatment" = rep(c("AGI", "DMSO"), 2)
                      )

ggplot(data=CD38_df[c(1:4),], aes(x=Cell.line, y=as.numeric(CD38), color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD38", x = "Cell lines")+
  theme_minimal()
```

## Replicat 2

```{r, echo=F}
CD38_rep2 <- data.frame("CD38" = c(887, 853, 6233,7747),
                        "Cell.line" = c("56-11", "56-11", "Molm14", "Molm14"),
                        "Treatment" = c("DMSO", "AGI", "DMSO", "AGI"))

ggplot(data=CD38_rep2, aes(x=Cell.line, y=as.numeric(CD38), color=factor(Treatment, levels = c("DMSO", "AGI"))))+
  scale_color_manual(values=c("#0000FF", "#FF0000"), limits=c("DMSO", "AGI")) +
  geom_bar(stat = "identity", fill = "white", position = position_dodge()) + 
  labs(color = "Treatment", title = "CD38", x = "Cell lines")+
  theme_minimal()
```

